
%-------------------------
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\classesList}[4]{
\item\small{
{#1 #2 #3 #4 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & \textbf{\small #2} \\
\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & \textbf{\small #2}\\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
{\Huge \scshape Luu Nam Dat} \\ \vspace{1pt}
alias: iluvgirlswithglasses \\ \vspace{1pt}
\small \raisebox{-0.1\height}\faPhone\ +847-0405-0027 ~ \href{mailto:lndat204@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{lndat204@gmail.com}} ~ 
\href{https://github.com/iluvgirlswithglasses}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/iluvgirlswithglasses}}
\vspace{-8pt}
\end{center}


%-----------ABOUT ME------------
\section{About Me}
I am Luu ``iluvgirlswithglasses'' Nam Dat, birthyear 2004. I am passionate about crafting solutions for challenging projects. Weekly reports irritate me as they make me spend time on other things than getting my job done.


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Science - VNUHCM}{October 2022 -- Today}
{Bachelor of Computer Science}{Ho Chi Minh City, Vietnam}
\resumeSubHeadingListEnd


%------AREAS OF EXPERTISE-------
\section{Areas of Expertise}
%\resumeSubHeadingListStart
\begin{multicols}{4}
\begin{itemize}[itemsep=-5pt, parsep=3pt]
\item\small Algorithmic Development
\item Data Structures
\item Mathematic Applications
\item Computer Vision
\item Systems Programming
\item Compiler Utilization
\item Operating Systems
\item Computer Architecture
\end{itemize}
\end{multicols}
\vspace*{2.0\multicolsep}
%\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Kc97ble (Free Contest)}{October 2021 -- October 2022}
{Backend Developer}{Ho Chi Minh City, Vietnam}
\resumeItemListStart
\resumeItem{Developed a web service to facilitate the renowned competitive programming contests.}
\resumeItem{Acquired proficiency in Typescript, NodeJS, and RESTful API development.}
\resumeItem{Demonstrated strong version control skills with Git, effectively collaborating in complex code bases, and consistently producing clean and high-quality source code.}
\resumeItemListEnd

\resumeSubheading
{SiGlaz VN Ltd.}{October 2022 -- Today}
{Computer Vision Scientist}{Ho Chi Minh City, Vietnam}
\resumeItemListStart
\resumeItem{Worked as an independent researcher.}
\resumeItem{Flawlessly integrated independent researches/projects into team project, regardless of the technological discrepancies.}
\resumeItem{Developed expertise in comprehending and creating complex technical articles and documents, contributing to the knowledge base of the organization.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}


%-----------PROJECTS-----------
\section{Remarkable Solo Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{EuphoAFIS} $|$ \emph{C++, CMake, Clang+LLVM, Unix, Windows, No 3rd-party}}{2023}
\resumeItemListStart
\resumeItem{A platform-independent, highly accurate \& performant automatic fingerprint identification system, meticulously optimized to the micro-architecture level of each device on which it is compiled.}
\resumeItem{Is capable of performing precise one-to-many matching within 1 second, in a database of 5 million fingerprints.}
\resumeItem{Was fully funded by SiGlaz VN Ltd.}
\resumeItem{Was deployed on Debian Linux Servers, Windows Servers, MacOS Servers, and AWS.}
\resumeItemListEnd
\vspace{-13pt}
\resumeProjectHeading
{\textbf{EuphoFP} $|$ \emph{C\#, .NET Core, .NET Framework, Unix, Windows, No 3rd-party}}{2023}
\resumeItemListStart
\resumeItem{A robust and reliable fingerprint feature extraction library, designed for .NET cross-platform development.}
\resumeItem{Has excellent resistance to noises and scratches; Is unaffected by the impact of pressure on the fingerprint impression; Has great tolerance to low-quality fingerprint images; Et cetera.}
\resumeItem{Was fully funded by SiGlaz VN Ltd.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Has profound knowledge of the language and the compiler of}{: C++} \\
\textbf{Proficient at}{: C\#, C, Python, Java, Typescript, Javascript, HTML/CSS} \\
\textbf{Technologies}{: Linux, Windows, Cloud Computing} \\
\textbf{Documentation Tools}{: LaTeX, (R) Markdown, Slides,...} \\
}}
\end{itemize}
\vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Extracurricular}
\resumeSubHeadingListStart
\resumeSubheading{Competitive Programming}{January 2021 -- October 2022}{}{Ho Chi Minh City}
\resumeItemListStart
\resumeItem{Accomplished outstanding achievements in regional contests and showed a strong performance in national competitions.}
\resumeItem{Possesses competent experience in international online tournaments.}
\resumeItem{Proven versatility in both solo and team-based competitive programming. Additionally, I can be a good teacher!}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}

